Coherent optical association of a single molecule -- Supplemental material

### 2020-11-09 sm.tex
Update on Overleaf.

\section{Calculating Matrix Elements with Coupled Channel Ground State}

Test Reference\cite{Liu2019}

>>>>

\section{Calculating Matrix Elements with Coupled Channel Ground State}
The free atom state (with spherically symmetric harmonic confinement) and target weakly-bound molecular state are calculated using coupled-channel methods. With the cylindrical symmetry present at non-zero magnetic field, the magnetic quantum number is a good quantum number. We use the $ \ket{F_{\text{Na}} = 2, m_{F_{\text{Na}}} = 2, F_{\text{Cs}} = 3, m_{F_{\text{Cs}}} = 3}$ spin combination, so states with total $ m_F = 5 $ are included. These states, written in the basis $ \ket{S, m_S, I, m_I}$, include $ \ket{0,0,5,5}, \ket{1,0$
